Empirical normative theories

### 2020-07-21 simple.tex
Removed \zar, not useful

\section{Additive single-answer empirical theories}
\subsection{Definition}
\commentOC{I leave the definition as is, but for the moment I only consider ${\gleadsto}$, a relation that does not depend on $i$; and I do not use $q(i)$.}
An empirical theory for a normative theory is a tuple $(q, (\gleadsto[q(i)])_{q(i) \in q(I)}, \gbeats, \alldargs, \dbeats, +)$,
with ${\gleadsto[q(i)]} \subseteq (\allargs × \Phi) \cap (\alldargs × \Phi)$, 
${\gbeats} \subseteq \allargs × \allargs$ and is irreflexive,
${\dbeats} \subseteq \alldargs × \allargs$ and is injective and its range includes $\gbeatsinv(\allargs)$, the domain of ${\gbeats}$ (thus $\forall \ar_1 \suchthat [\exists \ar_0 \suchthat \ar_1 \gbeats \ar_0]$: $\dbeatsinv(\ar_1)$ is a singleton). 
Define $\df \subseteq \allargs × \alldargs$ as $\df = \dbeatsinv \circ \gbeatsinv$. 
The symbol $+$ in an empirical theory stands for a function $+: \bigcup_{\ar \in \allargs}(\set{s} × \df(\ar)) → \allargs$.
As usual, $\ar + \ard$ means $+(\ar, \ard)$. 
Define $\dfp \subseteq \allargs × \allargs$ as, $\forall \ar \in \allargs$: $\dfp(\ar) = \ar + \df(\ar) = \set{\ar + \ard \suchthat \ard \in \df(\ar)}$.
An empirical theory must satisfy
$\exists k \in \N \suchthat \dfp^k(\dfp(\zar) \cup \gleadstoinv(\Phi)) = \emptyset$, where $\dfp^0$ is the identity function over $\allargs$.

@@

Given $i \in I, \phi \in \gPhi, \ar \in \allargs$, define the \emph{$\phi$-defensors of $\ar$ required for $i$}, $\di(\ar) \subseteq \alldargs$, as $\di(\ar) = [\dbeatsinv \circ {\ibeatsinv}](\ar)$. Define $\dip: \allargs → \allargs$ as $\dip(\ar) = \ar + \di(\ar)$.
Given $i \in I, \phi \in \gPhi$, define $\gargs[i, \phi] \subseteq \allargs$ as the transitive closure of ${\gleadstoinv}(\phi)$ under $\dip$: $\gargs[i, \phi] = \cup_{k \in \N} (\dip)^k(\dip(\zar) \cup {\gleadstoinv}(\phi))$.

>>>>

\section{Additive single-answer empirical theories}
\subsection{Definition}
\commentOC{I leave the definition as is, but for the moment I only consider ${\gleadsto}$, a relation that does not depend on $i$; and I do not use $q(i)$.}
An empirical theory for a normative theory is a tuple $(q, (\gleadsto[q(i)])_{q(i) \in q(I)}, \gbeats, \alldargs, \dbeats, +)$,
with ${\gleadsto[q(i)]} \subseteq (\allargs × \Phi) \cap (\alldargs × \Phi)$, 
${\gbeats} \subseteq \allargs × \allargs$ and is irreflexive,
${\dbeats} \subseteq \alldargs × \allargs$ and is injective and its range includes $\gbeatsinv(\allargs)$, the domain of ${\gbeats}$ (thus $\forall \ar_1 \suchthat [\exists \ar_0 \suchthat \ar_1 \gbeats \ar_0]$: $\dbeatsinv(\ar_1)$ is a singleton). 
Define $\df \subseteq \allargs × \alldargs$ as $\df = \dbeatsinv \circ \gbeatsinv$. 
The symbol $+$ in an empirical theory stands for a function $+: \bigcup_{\ar \in \allargs}(\set{s} × \df(\ar)) → \allargs$.
As usual, $\ar + \ard$ means $+(\ar, \ard)$. 
Define $\dfp \subseteq \allargs × \allargs$ as, $\forall \ar \in \allargs$: $\dfp(\ar) = \ar + \df(\ar) = \set{\ar + \ard \suchthat \ard \in \df(\ar)}$.
An empirical theory must satisfy
$\exists k \in \N \suchthat \dfp^k(\gleadstoinv(\Phi)) = \emptyset$, where $\dfp^0$ is the identity function over $\allargs$.

@@

Given $i \in I, \phi \in \gPhi, \ar \in \allargs$, define the \emph{$\phi$-defensors of $\ar$ required for $i$}, $\di(\ar) \subseteq \alldargs$, as $\di(\ar) = [\dbeatsinv \circ {\ibeatsinv}](\ar)$. Define $\dip: \allargs → \allargs$ as $\dip(\ar) = \ar + \di(\ar)$.
Given $i \in I, \phi \in \gPhi$, define $\gargs[i, \phi] \subseteq \allargs$ as the transitive closure of ${\gleadstoinv}(\phi)$ under $\dip$: $\gargs[i, \phi] = \cup_{k \in \N} (\dip)^k({\gleadstoinv}(\phi))$.
